Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-19 bdcloud_paper/latex/paper.tex
Added discussion and conclusion

\section{Discussion and Conclusion}
implementation
[want a modular framework with clearly-defined extension points, modularity so that users do not need to know about the machinations of the entire model, and so that modules are easy to develop and turn on/off dynamically]

[spark, hadoop ecosystem, parallelization of generating stores, customers, and transactions]

[model extensions]

>>>>

\section{Discussion and Conclusion}
We have described a domain-driven mathematical model and accompanying simulation for generating semantically-rich data.  We validated the method by analyzing generated data to inform decisions in a fictional advertising campaign. Scalability testing combined with analysis the implementation suggests that the data generation method can scale from small data sets appropriate for desktop development to large data sets for testing and benchmarking of clusters.

We see many opportunities for building on the work presented.  We intend to expand the model to incorporate additional factors.  Deeper integration of existing fields such as location and purchasing profiles (e.g., to model regional purchasing preferences) will increase the variety of the semantic information encoded in the generated data. The incorporation of weather and climate data can be used to influence when customers shop and the types of products they buy. For example, customers would be less likely to shop during snow storms and more likely to buy winter apparel for their pets. Modeling of time-dependent events such as sales, evolution of customer purchasing profiles over time, and ``life events,'' such as the birth or passing of pets, will enable more interesting time-series analysis of the data.

The current implementation was prototyped in Python.  We are working to implement the model using in Hadoop and Spark.  We will commit the resulting implementations to the Apache BigTop project to enable ease of access and immediate benefit to current users.
